Initial Analysis

### 2019-08-30 Initial_Analysis.Rmd
Determined RFMOs

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(Neighbor_List,
          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
          row.names = F)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO/",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Name = RFMO_nm_s)

>>>>

#### Grid cell information ####

# List of DBEM INDEX within the EEZ 
#Data provided by Vicki Lam

EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  EEZ_Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(EEZ_Neighbor_List,
          paste(Data_Path,"Spatial_Data/EEZ_Neighbor_List.csv", sep =""),
          row.names = F)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s)
